\documentclass[12pt]{article}
\usepackage{mathptmx}
\usepackage{setspace}
\usepackage[margin=1in]{geometry}
 
\begin{document}
 
\begin{doublespace}
 
\noindent \textbf{Andrew Ralph \quad Software Engineer \quad CRN:21962}
 
\bigskip
 
\noindent \textbf{Purpose Statement:} To inform you on software engineerings evolution and team leadership in the field.
 
\bigskip
 
\noindent \textbf{I. The Evolution of software engineering through AI}
 
\noindent \hspace{1em} A. Early days of software development
 
\noindent \hspace{1em} B. Impact of AI on the field
 
\bigskip
 
\noindent \textbf{II. Management and Leadership abilities within the Software Engineering field}
 
\noindent \hspace{1em} A. Project management methodologies
 
\noindent \hspace{1em} B. Team dynamics and communication
 
\noindent \hspace{1em} C. Training for management roles

\bigskip

\noindent \textbf{Conclusion: To conclude, AI is transfomring the way we think about software engineering, its able to make the more menial task more efficient and allows the poduction of our applications to be realised much quicker. With that said the managment of our teams is now the number one priority in our field simply because we need to be able to filter out the nonessentials when we are posting stuff to our final production. AI will make things more efficient but it is up to our teams to make sure we leave things as refined as possible.}

\newpage

\begin{center}
    \textbf{Works Cited}
\end{center}

\begin{center}
\textbf{Chechik, Marsha}, et al. ``Agentic AI in the Next Frontier of Model-Based Software Engineering: The Arrival of AI-Hyper-Agile Software Engineering Methods?'' \textit{Software and Systems Modeling}, April 2026, pp. 315--317.

\medskip

\textbf{Furda, Andrei}, et al. ``Jump-Starting Software Engineering Careers.'' \textit{IEEE Software}, September 2023, pp. 1--6.

\medskip

\textbf{Wasserman, Anthony I.} ``Preparing Software Engineers for Management Roles.'' \textit{IEEE Software}, September 2023, pp. 94--99.
\end{center}

\end{doublespace}
 
\end{document}

